\section{Closing}




\begin{frame}[label=ladila]{Philosophy}

KT is most naturally viewed in the context of panpsychism ('mind is everywhere', see Strawson, \cite{Goff:2019aa}), a particular, somewhat controversial version of the philosophy of consciousness.  \vfill

Idealism is another, perhaps more rigorous philosophical background (consciousness as the fundamental entity, 'mind is everything'). \vfill

 Although not necessary to explore the scientific implications of the theory, the adoption of these can be  motivated by simplicity, consistency criteria \citep{Symes2022-ri}.
 
\end{frame}




\begin{frame}[label=ladila]{Ethics}

 Agenthood carries with it aspects of morality associated to the role of the {\bf objective function} $O$. We can for example define notions of {\em good} or {\em evil} in computational terms based on the behavior of objective functions. \vfill
 
 For example, we may say that Agent's $A$ actions are {\em evil or morally wrong} for Agent $B$ if the objective function of $A$, $O_A$, increases when O$_B$ decreases, that is $O_A(O_B)$ is decreasing or  $O_A'(O_B) <0$.
 \vfill
 
 Conversely, we say that Agent $A$ actions are {\em good or morally right} for Agent $B$ if $O_A'(O_B) >0$. \vfill 

Synergistic behavior emerges when agents are good to each other, and mutually-destructive behavior takes place in the complementary case.  
 
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label=ladila]{Future}
Much work remains to be done! Will KT provide a unification framework for the different approaches to consciousness?\vfill

Can we evolve agents in computational frameworks? Are persistent patterns unavoidable (KT conjecture) in computation? Are there  types other than static (proton) and life? \vfill

Can we develop a theory bridging dynamical systems and AIT? \vfill

Can we discover the structure of reduced dynamics from data? \vfill

Can we design neurophenological methods to discover the structure of reports and behavior? \vfill

Can we design model-building agents mimicking life or intelligence? \vfill


\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label=ladila]{Thanks}
\vfill
\begin{center}
    Thanks for your attention and curiosity!  \\
    
    giulio.ruffini(at)neuroelectrics.com

\end{center}
\vfill

\end{frame}